Modelling the creation of ecological traps by environmentally persistent pathogens

### 2015-06-08 Manuscript/manuscript.tex
More descriptive captions

\begin{figure}
\centering
\caption{Differences between the median total effective population size of hosts on high quality patch distributions (quality between 0.76 and 1.77) and low quality patch distributions (quality between 0.23 to 1.24) as a function of disease-induced mortality ($\nu$) and the probability of direct transmission ($\delta$).  Reds indicate higher median host population sizes in high quality patch distributions, while blues indicate higher median host population sizes in low quality patch distributions.  Panel columns show low (0.3, a), medium (1.0, b), and high (3.2, c) pathogen longevities.}
\label{highvlow}
\end{figure}

\begin{figure}
\centering
\caption{Boxplots showing the range, over 100 replicate simulations, of susceptible (a), infectious (b), and total (c) host population sizes for high quality (red) and low quality (blue) habitat distributions.  Disease-induced mortality ($\nu$) and direct transmission rate ($\delta$) are fixed at values of 0.2 and 0.3, respectively.  Colored points show medians, while vertical lines indicate the outer-quartile ranges, with gray points indicating outliers (determined as points outside 1.5 times the inner-quartile range).}
\label{popsizes}
\end{figure}

\begin{figure}
\centering
\caption{Results from a single representative simulation with habitat quality uniformly distributed between 0.23 and 1.77, and a pathogen with a disease induced mortality of $\nu = 0.2$, a direct transmission rate of $\delta = 0.3$, and an envioronmental longevity equal to the expected residence time of a susceptible population on a unit quality patch (10 units of time here).  The top panel shows total proportion of patches occupied by susceptible (blue) and infectious (red) hosts over time.  The bottom panel shows the state -- susceptible (blue), infectious (red), or unoccupied (white) -- of individual patches through time.  Patches are stacked vertically with the lowest quality at the bottom and the highest quality at the top.}
\label{simvis}
\end{figure}

\begin{figure}
\centering
\caption{Boxplots showing the probability of infection (i.e. proportion of time occupied by infectious hosts) as a function of patch quality.  Panel columns show low (0.3, a, d), medium (1.0, b, e), and high (3.2, c, f) pathogen longevities, while rows show the effect of preferential selection of high quality habitat (a-c, $\xi_{im} = 0$,  no preference; d-f, $\xi_{im} = 0.5$, preference for high quality).  Black points show the median over 100 replicate simulations, while vertical lines show the outer-quartile range, and gray points indicate outliers. Disease induced mortality and probability of direct infection fixed at $\nu = 0.2$ and $\delta = 0.3$.}
\label{pinfection}
\end{figure}

\begin{figure}
\centering
\caption{Probability of host extinction as a function of pathogen environmental longevity and habitat preference, with black showing no habitat preference ($\xi_{im} = 0$) and red showing preference for high quality habitat ($\xi_{im} = 0.5$).  Disease induced mortality and probability of direct infection fixed at $\nu = 0.2$ and $\delta = 0.3$.}
\label{pext}
\end{figure}
\clearpage

>>>>

\begin{figure}
\centering
\caption{Differences between the median total effective population size of hosts on low quality patch distributions (quality between 0.23 to 1.24) and high quality patch distributions (quality between 0.76 and 1.77) as a function of disease-induced mortality ($\nu$) and the probability of direct transmission ($\delta$).  Reds indicate that high quality habitat distributions support higher median host population sizes than low quality habitat, primarily corresponding to pathogens with either very limited or very extensive spread. Conversely, blues indicate higher median host population sizes on low quality habitat distributions, corresponding to pathogens with intermediate levels of spread.  Panel columns show low (0.3, a), medium (1.0, b), and high (3.2, c) pathogen longevities.}
\label{highvlow}
\end{figure}

\begin{figure}
\centering
\caption{Boxplots showing the range, over 100 replicate simulations, of susceptible (a), infectious (b), and total (c) host population sizes for high quality (red) and low quality (blue) habitat distributions.  Disease-induced mortality ($\nu$) and direct transmission rate ($\delta$) are fixed at values of 0.2 and 0.3, respectively.  Colored points show medians, while vertical lines indicate the outer-quartile ranges, with gray points indicating outliers (determined as points outside 1.5 times the inner-quartile range).  At low longevities, this pathogen is largely unable to persist and high quality habitat supports larger populations of susceptible hosts.  However, low quality habitat is better able to maintain these susceptible hosts as the pathogen's longevity increases, leading to larger total population sizes.}
\label{popsizes}
\end{figure}

\begin{figure}
\centering
\caption{Results from a single representative simulation with habitat quality uniformly distributed between 0.23 and 1.77, and a pathogen with a disease induced mortality of $\nu = 0.2$, a direct transmission rate of $\delta = 0.3$, and an envioronmental longevity equal to the expected residence time of a susceptible population on a unit quality patch (10 units of time here).  The top panel shows total proportion of patches occupied by susceptible (blue) and infectious (red) hosts over time.  The bottom panel shows the state -- susceptible (blue), infectious (red), or unoccupied (white) -- of individual patches through time.  Patches are stacked vertically with the lowest quality at the bottom and the highest quality at the top.  Note the overall more consistent occupancy on high quality habitat and the only very brief spurts of infectious occupancy on low quality habitat.}
\label{simvis}
\end{figure}

\begin{figure}
\centering
\caption{Boxplots showing the probability of infection (i.e. proportion of time occupied by infectious hosts) as a function of patch quality.  Panel columns show low (0.3, a, d), medium (1.0, b, e), and high (3.2, c, f) pathogen longevities, while rows show the effect of preferential selection of high quality habitat (a-c, $\xi_{im} = 0$,  no preference; d-f, $\xi_{im} = 0.5$, preference for high quality). The bottom row demonstrates the existence of an ecological trap on high quality habitat resulting from the fitness costs of increased disease risk. Black points show the median over 100 replicate simulations, while vertical lines show the outer-quartile range, and gray points indicate outliers. Disease induced mortality and probability of direct infection fixed at $\nu = 0.2$ and $\delta = 0.3$.}
\label{pinfection}
\end{figure}

\begin{figure}
\centering
\caption{Probability of host extinction as a function of pathogen environmental longevity and habitat preference, with black showing no habitat preference ($\xi_{im} = 0$) and red showing preference for high quality habitat ($\xi_{im} = 0.5$).  Disease induced mortality and probability of direct infection fixed at $\nu = 0.2$ and $\delta = 0.3$.  The combination of preference for high quality habitat and an environmentally long-lived pathogen serve to substantially increase extinction risk.}
\label{pext}
\end{figure}
\clearpage
